\bibitem[HeJoBu 84] {hejobu 84} M. Heideman, D. Johnson and C. Burrus: {\sl Gauss and the history of the fast fourier transform}; IEEE ASSP Magazine, vol. 1, no. 4, October 1984.
\bibitem[KreNor 11] {krenor 11} E. Kreyszig, H. Kreyszig, und E. Norminton: {\sl Advanced Engineering Mathematics}; Wiley, 10 Edition, 2011.
\bibitem[Scho 05] {scho 05} Arthur L. Schoenstadt: {\sl An Introduction to Fourier Analysis Fourier Series, Partial Diﬀerential Equations
and Fourier Transforms
}; Department of Applied Mathematics Naval Postgraduate School, 2005.
\bibitem[Ser 17] {ser 17} Valery Serov: {\sl Fourier Series, Fourier Transform and Their Applications to Mathematical Physics}; Springer Verlag, 2017.
\bibitem[Sig 07] {sig 07} U. Sigrist: {\sl “Optimizing parallel 3D fast Fourier transformations for a
cluster of IBM POWER5 SMP nodes}; Ph.D. Dissertation, The University of Edinburgh, Aug 2007.
\bibitem[SHaHe 14] {shahe 14}J. Sheng, B. Humphries, H. Zhang and M. C. Herbordt: {\sl Design of 3D FFTs with FPGA Clusters}; IEEE High Performance Extreme Computing Conference (HPEC), 2014.
\bibitem[Aya 19] {aya 19} Ayala A., S. Tomov, X. Luo, H. Shaiek, A. Haidar, G. Bosilca, and J. Dongarra: {\sl Impacts of Multi-GPU MPI Collective Communications on Large FFT Computation}; Workshop on Exascale MPI (ExaMPI) at SC19, 2019.
\bibitem[Sha 19] {sha 19} Shaiek, H., S. Tomov, A. Ayala, A. Haidar, and J. Dongarra:{\sl GPUDirect MPI Communications and Optimizations to Accelerate FFTs on Exascale Systems}; ICL, 2019.
\bibitem[And 12] {and 12}André Neubauer: {\sl DFT – Diskrete Fourier-Transformation Elementare Einführung}; Springer Vieweg, 2012
